### 2014-06-19 alex/2020.Rmd
some stuff

While looking at my favorite country with a city named Tirana, I noticed that something strange was happening.  No other country appears to have this.
```{r albania, cache=TRUE}
#peak at 54 hours
qplot(OUTHOURS, data = subset(student2012, CNT == "Albania"))
```

@@

Compare differences in the top 20 and bottom 20 math scores for each nation
```{r math, cache=TRUE}
student2012 %>%
  select(CNT, math, OUTHOURS) %>%
  group_by(CNT) %>%

  filter(math < quantile(math, probs = seq(0, 1, 0.2))[2] | 
         math > quantile(math, probs = seq(0, 1, 0.2))[5])
```

>>>>

While looking at my favorite country with a city named Tirana, I noticed that something strange was happening.  No other country appears to have this.
```{r albania, echo=FALSE, cache=TRUE}
library(ggplot2)
#peak at 54 hours
qplot(OUTHOURS, data = subset(student2012, CNT == "Albania"))
```

@@

Compare differences in the top 20 and bottom 20 math scores for each nation.
```{r math, cache=TRUE}
student2012$ST69Q02 = as.numeric(student2012$ST69Q02)
student2012$ST70Q02 = as.numeric(student2012$ST70Q02)

math2020 = student2012 %>%
            select(CNT, math, OUTHOURS, ST69Q02, ST70Q02, #minutes studying, class periods
                   ST44Q01, ST44Q03, ST44Q04,ST44Q05, ST44Q07, ST44Q08, #attributions to failure
                   ST15Q01, ST19Q01) %>% #job status for parents
            group_by(CNT) %>%
            mutate(top20 = math > quantile(math, probs = seq(0, 1, 0.2))[5]) %>%
            filter(math < quantile(math, probs = seq(0, 1, 0.2))[2] | 
                   math > quantile(math, probs = seq(0, 1, 0.2))[5])
```

```{r math2, eval=TRUE}
library(ggplot2)

#Attributions to Failure - Not Good at Maths Problems
qplot(x = ST44Q01, fill = top20, data = subset(math2020, !is.na(ST44Q01)), geom = "bar", position = "fill")

#Attributions to Failure - Teacher Did Not Explain Well
qplot(x = ST44Q03, fill = top20, data = subset(math2020, !is.na(ST44Q03)), geom = "bar", position = "fill")

#Attributions to Failure - Bad Guesses
qplot(x = ST44Q04, fill = top20, data = subset(math2020, !is.na(ST44Q04)), geom = "bar", position = "fill")

#Attributions to Failure - Material Too Hard
qplot(x = ST44Q05, fill = top20, data = subset(math2020, !is.na(ST44Q05)), geom = "bar", position = "fill")

#Attributions to Failure - Teacher Didnt Get Students Interested
qplot(x = ST44Q07, fill = top20, data = subset(math2020, !is.na(ST44Q07)), geom = "bar", position = "fill")

#Attributions to Failure - Unlucky
qplot(x = ST44Q08, fill = top20, data = subset(math2020, !is.na(ST44Q08)), geom = "bar", position = "fill")

#Father Current Job Status
qplot(x = ST19Q01, fill = top20, data = subset(math2020, !is.na(ST19Q01)), position = "fill")

#mother current job status
qplot(x = ST15Q01, fill = top20, data = subset(math2020, !is.na(ST15Q01)), position = "fill")

#hours studied
qplot(x = OUTHOURS, fill = top20, data = subset(math2020, !is.na(OUTHOURS)), position = "fill")
```
